---
title: "Exercises 7"
author: "Alyssa Bigness"
date: "3/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(shiny)
```


10.1 Basic Reactivity
Read Sections 3.1 through 3.3 in the Basic Reactivity Chapter of Mastering Shiny

Exercise 1. 3.3.6 Exercise 1 in Mastering Shiny.

1. Given this UI:
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
```

Fix the simple errors found in each of the three server functions below. First try spotting the problem just by reading the code; then run the code to make sure you’ve fixed it.

```{r}
server1 <- function(input, output, server) {
  output$greeting <- renderText(string())
  string <- reactive(paste0("Hello ", input$name))
}

server2 <- function(input, output, server) {
  output$greeting <- renderText(greeting)
  greeting <- paste0("Hello ", input$name)
}

server3 <- function(input, output, server) {
  output$greeting <- renderText({
    paste0("Hello", input$name)
  })
}
```




Exercise 2. 3.3.6 Exercise 2 in Mastering Shiny.

2. Draw the reactive graph for the following server functions:

```{r}
server1 <- function(input, output, session) {
  c <- reactive(input$a + input$b)
  e <- reactive(c() + input$d)
  output$f <- renderText(e())
}
```
f <- e <- c <- a
            <- b
            
       <- d

```{r}
server2 <- function(input, output, session) {
  x <- reactive(input$x1 + input$x2 + input$x3)
  y <- reactive(input$y1 + input$y2)
  output$z <- renderText(x() / y())
}
```
z <- x <- x1
       <- x2
       <- x3
       
  <- y <- y1
       <- y2

```{r}
server3 <- function(input, output, session) {
  d <- reactive(c() ^ input$d)
  a <- reactive(input$a * 10)
  c <- reactive(b() / input$c) 
  b <- reactive(a() + input$b)
}
```
d <- c <- b <- a