---
title: "Exercises 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

6.6 Supplementary Exercises
Consider again the Happy Planet Index data that we worked with in Section 5.2 It may be helpful to reread the description of the data set.

```{r}
library(tidyverse)
hpi_df <- read_csv("data/hpi-tidy.csv")
```

Exericse 1. Make a map of a variable of your choosing. In coord_map(), use projection = "mercator", which is also the default (we will see in a later exercise that this probably is not the best choice).

Hint: in ggplot2’s map_data() function, there is a built in map of the "world".

Hint: You can read more about projections in Section 17.3.2 of Modern Data Science with R

```{r}
library(maps)
world_df <- ggplot2::map_data("world")



ggplot(data = world_df,
       mapping = aes(x = long, y = lat, group = group)) + geom_polygon() + coord_map(projection = "mercator")
```





Exercise 2. You may notice that the United States does not get coloured in your map. Examine this issue further and fix the map so that the United States is coloured.

```{r}
us <- filter(world_df, region == "USA")

ggplot(data = world_df,
       mapping = aes(x = long, y = lat, group = group)) + geom_polygon(colour = "black")  + geom_polygon(data = us, aes(x = long, y = lat, group = group), fill = "red") + coord_map(projection = "mercator")
```



Exercise 3. You may have noticed that there are two horizontal stripes across your map. This is an issue that drove me nuts! Check out this submitted issue on ggplot2’s GitHub page for the reason for the error as well as a fix. Use it to fix your plot.

```{r}
ggplot(data = world_df,
       mapping = aes(x = long, y = lat, group = group)) + geom_polygon(colour = "black")  + geom_polygon(data = us, aes(x = long, y = lat, group = group), fill = "red") + coord_map(xlim = c(-180,180))
```



Exercise 4. Read about Mercator projections in this blog post. What does this source say about the sizes of Greenland vs. Africa in a Mercator projection.
This source says that the size of Greenland is 550% too big and that Greenland shoud be able to fit into Africa 14 times.


Exercise 5. Examine all of the different options for map projection with ?mapproject. Then, change the projection to "globular". Change the projection again to "gilbert". How does the relative size of Greenland to Africa change in the projections?

```{r}
ggplot(data = world_df,
       mapping = aes(x = long, y = lat, group = group)) + geom_polygon(colour = "black")  + geom_polygon(data = us, aes(x = long, y = lat, group = group), fill = "red") + coord_map(projection = "globular", xlim = c(-180,180))


ggplot(data = world_df,
       mapping = aes(x = long, y = lat, group = group)) + geom_polygon(colour = "black")  + geom_polygon(data = us, aes(x = long, y = lat, group = group), fill = "red") + coord_map(projection = "gilbert", xlim = c(-180,180))

```
The relative size of Greenland to Africa changes in these projections by making Greenland way smaller than Africa like it is suppose to be, showing a more accurate map of the size of Greenland.

You can read more about projections in R at this site. There’s definitely a lot going on, and you should always consider what map projection you are using when mapping data, especially if that data is on a global scale!