---
title: "Midterm Take-Home Mini-Tutorial 4"
author: "Alyssa Bigness"
date: "3/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Mini-Tutorial 4: shiny (20 points)

Topics to Cover:

An Introduction to shiny

An Introduction to Reactivity

You should use a data set other than the data set you chose for the take-home quiz 6.

Make Sure to Include:

(4 points) An introductory statement with the goal of the section (in your own words) and a brief description of the data set and variables you will be using.

(16 points) R code chunks interspersed with some text descriptions about the code you have written and with text description about each topic. At the end of this tutorial, the person reading it should be able to construct a shiny app with real data.

Introduction:
The goal of this section is to introduce the Shiny package which allows users to create interactive web apps and learn how reactive graphs are useful. The data set I will be using is the alcohol.csv.
The variables I will be using are the country, beer servings, wine servings, spirit servings, and total litres of pure alcohol.

```{r}
library(tidyverse)
alcohol_df <- read_csv("data/alcohol.csv")
```


This app will let the user choose a country, a statistic, and the number of bins in order to create a geom_col of the information given by the user, using the alcohol data set.
```{r}
library(shiny)

var_choices <- names(alcohol_df)[c(2:5)]
ui <- fluidPage(
  sidebarLayout(sidebarPanel(
    selectInput("countrychoice",
                   label = "Choose a Country", 
                   choices = levels(factor(alcohol_df$country))),
    radioButtons("varchoice", label = "Choose a Statistic",
                 choices = var_choices),
    sliderInput("binnumber", label = "Choose a Number of Bins", 
                min = 1, max = 50, value = 15, step = 1)),
    mainPanel(plotOutput("histgraph"))
  )
)




server <- function(input, output, session) {
  df_sub <- reactive({
    alcohol_df %>% filter(country == input$countrychoice)
  })
  
  hist_plot <- reactive({
    # ggplot(df_sub(), aes_string(x = input$varchoice)) +
    # geom_histogram(colour = "black", fill = "white", bins = 15)
    base_plot <- ggplot(df_sub(), 
                        aes(x = input$countrychoice, 
                            y= .data[[input$varchoice]]))
    base_plot + geom_col(colour = "black", fill = "white",
                                 bins = input$binnumber) +
        theme_minimal(base_size = 22)
  
   
  })
  
  output$histgraph <- renderPlot({
    hist_plot()
  })

  
  
}

shinyApp(ui, server)
```




