---
title: "Midterm Take-Home Mini-Tutorial 2"
author: "Alyssa Bigness"
date: "3/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Mini-Tutorial 2: Mapping (15 points)

Topics to Cover:

Either mapping with the maps package OR mapping from a shapefile. Many shapefiles can be found at https://www.census.gov/geographies/mapping-files/time-series/geo/carto-boundary-file.html
Make sure to include:

(4 points) An introductory statement with the goal of the section (in your own words) and a brief description of the data set and variables you will be using.

(11 points) R code chunks interspersed with some text descriptions about the code you have written and with text description about each topic. If you are using the maps package, you should use a map other than the U.S. States Map or World Map that we used in class.


Introduction:
The goal of this section is to show how to create a map in R using the maps library. The data set I will be using is france_df which is a map of france from the maps package. The variables I will be using from the dataset is the long (longitude), lat (latitude), order, and region.


The maps package has pre-drawn maps for parts of the world, for example we will be using the France map in this part of the tutorial.
```{r}
## install.packages("maps")
library(maps)
library(tidyverse)

france_df <- ggplot2::map_data("france")
france_df %>% nrow

ggplot(data = france_df,
            mapping = aes(x = long, y = lat,
                          group = group)) +
  geom_polygon(fill = "white", color = "black")  +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) + 
  theme_void()
```
We use geom_polygon() and the group aesthetic to tell R Studio how to create the boundaries of France. The albers projection for the coord_map shows areas accurately but distorts the shapes, while the theme_void() removes the x axis and y axis and their tick marks.

