---
title: "Quiz 4 In-Class"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Quiz 4 In-Class
Complete this quiz in a .Rmd file. To turn in the quiz, push both a .Rmd file and a knitted .html file to your GitHub site.

Statement of Integrity: Copy and paste the following statement and then sign your name (by typing it) on the line below.

“All work presented is my own. I have not communicated with or worked with anyone else on this quiz.”

Collaboration Reminder: You may not communicate with or work with anyone else on this quiz, but you may use any of our course materials or materials on the Internet.



Question 1 (20 points). Examine the alcohol.csv data set that you may have used as an introductory data set in STAT/DATA 234:

```{r}
library(tidyverse)
library(here)
library(maps)
world_df <- ggplot2::map_data("world")
alcohol_df <- read_csv(here("data/alcohol.csv"))
world_full <- full_join(world_df, alcohol_df , by = c("region" = "country"))
```

The data set has the following variables on countries throughout the world:
country, the name of the country
beer_servings, the number of beer servings per person per year
spirit_servings, the number of spirit servings per person per year
wine_servings, the number of wine servings per person per year
total_litres_of_pure_alcohol, the number of litres of pure alcohol consumed per person per year
Construct a map of the beer_servings variable. You should choose an appropriate projection and change the default colour scheme of your map.

```{r}
ggplot(data = world_full,
       mapping = aes(x = long, y = lat, group = group)) + geom_polygon(colour = "black")  + geom_polygon(data = world_full, aes(x = long, y = lat, group = group, fill = beer_servings)) + coord_map(xlim = c(-180,180), projection = "mercator")

```



Question 2 (5 points). Give an example of a question of interest about the alcohol data where you would want to construct a visualization other than a map to answer the question. What type of visualization would you construct instead?

An example about alcohol data where you would want to construct a visualization other than a map would be a bar graph showing each countries alcohol serving for each type of alcohol.

